Prefetching SPARQL query cacher

### 2016-05-03 dissertation/cache-proxy.tex
more on the arrows

\begin{figure}
\begin{center}
\begin{tikzpicture}
\draw (0,0) --(4,0);
\node at (5.5,0) { Database cache };
\draw (0,0.5) --(4,0.5);
\node at (5.5,0.5) { Reverse proxy };
\draw (0,2) --(4,2);
\node at (5.5,2) { Caching proxy };
\draw (0,3.5) --(4,3.5);
\node at (5.5,3.5) { Forward proxy };
\draw (0,4) --(4,4);
\node at (5.5,4) { Client cache };
\end{tikzpicture}
\caption{The possible positions of a cache. A cache may reside at both
  the server side or client side, or any of the intermediate
  proxies. The database proxy and reverse proxy is typically
  controlled by the data provider.}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\begin{tikzpicture}
\draw (0,0) --(4,0);
\node at (5.5,0) { Database };
\draw (0,0.5) --(4,0.5);
\node at (5.5,0.5) { Reverse proxy };
\draw (0,2) --(4,2);
\node at (5.5,2) { Caching proxy };
\draw (0,3.5) --(4,3.5);
\node at (5.5,3.5) { Forward proxy };
\draw (0,4) --(4,4);
\node at (5.5,4) { Client cache };

\draw [->] (0.2,4) --(0.2,0);
\draw [<-] (0.4,4) --(0.4,0);
\draw [->] (0.7,2) --(0.7,0);
\draw [<-] (0.9,2) --(0.9,0);
\draw [->] (1.2,4) --(1.2,2);
\draw [dashed, ->] (1.2,2) --(1.2,0);
\draw [dashed, <-] (1.4,2) --(1.4,0);
\draw [->] (1.5,2) --(1.5,4);
\draw [->] (1.7,2) --(1.7,0);
\draw [<-] (1.9,2) --(1.9,0);
\draw [->] (2.2,4) --(2.2,2);
\draw [->] (2.4,2) --(2.4,4);
\end{tikzpicture}
\caption{The possible positions of a cache. A cache may reside at both
  the server side (as a database cache) or client side, or any of the
  intermediate proxies. The database cache and reverse proxy is
  typically controlled by the data provider. The arrows illustrate
  requests (when pointing down) and responses (when pointing up) in a
  deployment scenario for when a the query cache considered in this
  paper is deployed on a caching proxy in the Internet infrastructure,
  see the text for details.}
\end{center}
\end{figure}
